Response to reviewers

### 2024-11-28 Manuscript/ecography_reponse_letter.tex
Update ecography_reponse_letter.tex

% We have rewritten the last paragraph of the introduction to include the following:
%  \textit{Beyond simulations, we also used an empirical dataset of Hawaiian bird traits and looked at how anthropogenic pressures have shaped the trait space (mechanism; why) based extinction events on Hawaiian islands before and after the year 1500 (process; how) and how different metrics (pattern; what) can lead to different interpretations of the data.}
%  \textit{We show that, with a fixed process and mechanisms approximation, the choice of the statistic to describe the pattern (the disparity or functional diversity metrics) has a great impact on the interpretation of the data with the exact same data being sometimes interpreted in opposite ways.}
%  \textit{We suggest caution when summarising patterns in observed data and propose a pipeline and tools for researchers to help understand how their pattern (often stemming from multidimensional data) can vary intuitively or not depending on the process and mechanism of interest.}
%  Lines @@@

>>>>

We have rewritten the last paragraph of the introduction to include the following:

\textit{To apply our framework to a realistic context, we also used an empirical dataset of Hawaiian bird traits and looked at how anthropogenic pressures have shaped the trait space (mechanism; why) based on extinction events on Hawaiian islands before and after the year 1500 (process; how), and how different metrics (pattern; what) can lead to different interpretations of the data.
We show that, with a fixed process and mechanisms approximation, the choice of statistic to describe the pattern (the disparity or functional diversity metrics) has a great impact on the interpretation of the data, with the exact same data being sometimes interpreted in opposite ways.}
Lines 114-122.

\textit{We suggest caution when summarising patterns in observed data and propose a pipeline and tools for researchers to help understand how their pattern (often stemming from multidimensional data) can vary intuitively or not depending on the process and mechanism of interest.}
Lines 570-573.
